InteroceptionScale (study 2) - Data Analysis

### 2025-02-04 study2/analysis/2_analysis.qmd
todo

---
title: "InteroceptionScale - Data Analysis"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
execute: 
  cache: true
---

@@

df <- read.csv("../data/data_participants.csv")

items <- select(df, contains("_Q")) 
byfacet <- items[df$Condition=="Dimensions",]
bymodality <- items[df$Condition=="Domains",]
byrandom <- items[df$Condition=="Random",]
```

```{r}
labels <- list(
  Sexual_State_Q1 = "I always know when I am sexually aroused",
  Sexual_State_Q2 = "I always feel in my body if I am sexually aroused",
  Sexual_State_Q3 = "My body is always in the same specific state  when I am sexually aroused",
  Sexual_State_Q4 = "Being sexually aroused is a very different bodily feeling compared to other states (e.g., feeling anxious, relaxed, or after physical exercise)",
  Sexual_State_Q5 = "I can always tell that I am sexually aroused from the way I feel inside",
  Sexual_State_A = "I always know that I am attentively doing a study",
  Sexual_Cardiac_Q1 = "When I am sexually aroused, I often feel changes in the way my heart beats (e.g., faster or stronger)",
  Sexual_Respiratory_Q1 = "When I am sexually aroused, I often feel changes in my breathing (e.g., faster, shallower, or less regular)",
  Sexual_Gastric_Q1 = "When I am sexually aroused, I often feel changes in my stomach (e.g., bloating, rumbling, discomfort)",
  Sexual_Gastric_Q2 = "When I am sexually aroused, I often feel butterflies in my stomach",
  Sexual_Genital_Q1 = "When I am sexually aroused, I often notice specific sensations in my genital area (e.g., tingling, warmth, wetness, stiffness, pulsations)",
  Sexual_Genital_Q2 = "During sex or masturbation, I often feel very strong sensations coming from my genital areas",
  Sexual_SkinThermo_Q1 = "When I am sexually aroused, I often feel changes in my temperature (e.g., feeling warm or cold)",
  Sexual_SkinThermo_Q2 = "When I am sexually aroused, I often feel like some areas of my skin become sweaty (e.g., palms, back, forehead)",
  Sexual_SkinThermo_Q3 = "When I am sexually aroused, I often feel my mouth becoming dry",
  Sexual_ColonBladder_Q1 = "When I am sexually aroused, I often feel like I need to relieve myself by urinating or defecating",
  Sexual_ColonBladder_Q2 = "During sex or masturbation, I often feel like I need to relieve myself by urinating or defecating",
  Anxious_State_Q1 = "I always know when I am anxious",
  Anxious_State_Q2 =  "I always feel in my body if I am anxious",
  Anxious_State_Q3 = "My body is always in the same specific state when I am anxious",
  Anxious_State_Q4 = "Being anxious is a very different bodily feeling compared to other states (e.g., feeling sexually aroused, relaxed or after exercise)",
  Anxious_State_Q5 = "I often realize that I am anxious only when others tell me",
  Anxious_Cardiac_Q1 = "When I am anxious, I often feel changes in the way my heart beats (e.g., faster or stronger)",
  Anxious_Respiratory_Q1 = "When I am anxious, I often feel changes in my breathing (e.g., faster, shallower, or less regular)",
  Anxious_Gastric_Q1 = "When I am anxious, I often feel changes in my stomach (e.g., bloating, rumbling, discomfort)",
  Anxious_Genital_Q1 = "When I am anxious, I often notice specific sensations in my genital area (e.g., contractions, dryness)",
  Anxious_SkinThermo_Q1 = "When I am anxious, I often feel changes in my temperature (e.g., feeling warm or cold)",
  Anxious_SkinThermo_Q2 = "When I am anxious, I often feel like some areas of my skin become sweaty (e.g., palms, back, forehead)",
  Anxious_SkinThermo_Q3 = "When I am anxious, I often feel my mouth becoming dry",
  Anxious_SkinThermo_Q4 = "When I am anxious, I often have difficulty swallowing",
  Anxious_SkinThermo_A = "Even if I am anxious, I should now answer all the way to the left",
  Anxious_ColonBladder_Q1 = "When I am anxious, I often feel like I need to relieve myself by urinating or defecating",
  Nociception_State_Q1 = "I always feel in my body if I am ill",
  Nociception_State_Q2 =  "I can easily tell when I am feeling ill (e.g., nauseous or sick)",
  Nociception_Cardiac_Q1 = "I often feel painful sensations coming from my heart",
  Nociception_Cardiac_Q2 = "I often experience painful sensations coming from my chest",
  Nociception_Respiratory_Q1 = "I often feel like I have difficulties breathing normally",
  Nociception_Respiratory_Q2 = "I often feel like I can't get enough oxygen by breathing normally",
  Nociception_Gastric_Q1 = "I often feel pain in my stomach",
  Nociception_Genital_Q1 = "My genital organs are very sensitive to pleasant stimulations",
  Nociception_Genital_Q2 = "My genital organs are very sensitive to painful stimulations",
  Nociception_SkinThermo_Q1 = "My skin is very sensitive to painful stimulations (e.g., pinching)",
  Nociception_SkinThermo_Q2 = "My skin is very sensitive to pleasant stimulations (e.g., caressing)",
  Nociception_SkinThermo_Q3 = "Changes in temperature (e.g., feeling feverish or cold) are the first things I notice when I am becoming ill",
  Nociception_ColonBladder_Q1 = "I often experience a pleasant sensation when relieving myself when urinating or defecating)",
  Nociception_ColonBladder_Q2 = "I often experience painful sensations when relieving myself when urinating or defecating",
  Nociception_ColonBladder_A = "I often experience sensations, and I will answer zero to this question",
  Sensitivity_State_Q1 =  "I always know when I am relaxed",
  Sensitivity_State_Q2 =  "I always feel in my body if I am relaxed",
  Sensitivity_State_Q3 = "My body is always in the same specific state when I am relaxed",
  Sensitivity_State_Q4 = "Being relaxed is a very different bodily feeling compared to other states (e.g., feeling anxious, sexually aroused or after exercise)",
  Sensitivity_State_Q5 = "When something important is happening in my life, I can feel it in my body",
  Sensitivity_Cardiac_Q1 = "In general, I am very sensitive to changes in my heart rate",
  Sensitivity_Cardiac_Q2 = "I often notice changes in my heart rate",
  Sensitivity_Cardiac_Q3 = "I can notice even very subtle changes in the way my heart beats",
  Sensitivity_Cardiac_Q4 = "I am always very aware of my heartbeats, even when I am calm",
  Sensitivity_Cardiac_Q5 = "I only notice my heart when it is thumping in my chest",
  Sensitivity_Cardiac_Q6 = "I often try to feel my heart with my hands (e.g., by putting my hand on my chest)",
  Sensitivity_Cardiac_Q7 = "When something important is happening in my life, I can feel immediately feel changes in my heart rate",
  Sensitivity_Cardiac_A = "In general, I am very sensitive and attentive to the questions I am currently answering",
  Sensitivity_Respiratory_Q1 = "In general, I am very sensitive to changes in my breathing",
  Sensitivity_Respiratory_Q = "I often notice changes in my breathing",
  Sensitivity_Respiratory_Q3 = "I can notice even very subtle changes in my breathing",
  Sensitivity_Respiratory_Q4 = "I am always very aware of how I am breathing, even when I am calm",
  Sensitivity_Respiratory_Q5 = "I often only notice how I am breathing when it becomes loud",
  Sensitivity_Respiratory_Q6 = "I often only notice how I am breathing when my breathing becomes shallow or irregular",
  Sensitivity_Respiratory_Q7 = "When something important is happening in my life, I can immediately feel changes in my breathing",
  Sensitivity_Gastric_Q1 = "In general, I am very sensitive to what my stomach is doing",
  Sensitivity_Gastric_Q2 = "I can notice even very subtle changes in what my stomach is doing",
  Sensitivity_Gastric_Q3 = "I am always very aware of what my stomach is doing, even when I am calm",
  Sensitivity_Gastric_Q4 = "I often check the smell of my own breath",
  Sensitivity_Gastric_Q5 = "I often check the smell of my farts",
  Sensitivity_Gastric_Q6 = "I often pay attention to the noises of my stomach",
  Sensitivity_Gastric_A = "I often pay attention to the answers I am giving",
  Sensitivity_Genital_Q1 = "In general, I am very sensitive to changes in my genital organs",
  Sensitivity_Genital_Q2 = "I can notice even very subtle changes in the state of my genital organs",
  Sensitivity_Genital_Q3 = "I am always very aware of the state of my genital organs, even when I am calm",
  Sensitivity_SkinThermo_Q1 = "In general, my skin is very sensitive",
  Sensitivity_SkinThermo_Q2 = "I can notice even very subtle stimulations to my skin (e.g., very light touches)",
  Sensitivity_SkinThermo_Q3 =  "I can notice even very subtle changes if my skin becomes dry or sweaty",
  Sensitivity_SkinThermo_Q4 ="I am always very aware if my hands and feet are cold or warm",
  Sensitivity_SkinThermo_Q5 = "I often check the smell of my armpits",
  Sensitivity_SkinThermo_Q6 = "I am very prone to having goosebumps",
  Sensitivity_SkinThermo_Q7 ="My skin is susceptible to itchy fabrics and materials",
  Sensitivity_SkinThermo_Q8 = "I enjoy the sensations of touching different materials (e.g., soft fabrics, wooden objects, smooth surfaces)",
  Sensitivity_ColonBladder_Q1 = "In general, I am very aware of the sensations that are happening when I am defecating",
  Sensitivity_ColonBladder_Q2 = "In general, I am very aware of the sensations that are happening when I am urinating",
  Sensitivity_ColonBladder_Q3 = "I often check the colour of my urine",
  Sensitivity_ColonBladder_Q4 =  "I often check the colour of my faeces",
  Accuracy_State_Q1 =  "I can always accurately feel when I am about to cough",
  Accuracy_State_Q2 = "I can always accurately feel when I am about to sneeze",
  Accuracy_State_Q3 = "I can always accurately feel when I am about to vomit",
  Accuracy_State_Q4 = "I can always accurately feel when I am starting to be hungry",
  Accuracy_State_Q5 = "I can always accurately feel when I am starting to be thirsty",
  Accuracy_Cardiac_Q1 = "I can always accurately feel if my heart rate is slow or fast",
  Accuracy_Cardiac_Q2 = "I sometimes feel like my heart is racing or beating faster than usual, but when I check my pulse, it is not as intense as I thought",
  Accuracy_Respiratory_Q1 = "I can always accurately feel how I am breathing (e.g., fast or slow, deep or shallow)",
  Accuracy_Respiratory_A = "I can always accurately answer to the left on this question to show that I am reading it",
  Accuracy_Gastric_Q1 = "I can always accurately feel when I am about to fart",
  Accuracy_Gastric_Q2 = "I can always accurately feel when I am about to burp",
  Accuracy_Gastric_Q3 = "I often feel thirsty even if I drank recently",
  Accuracy_Gastric_Q4 = "I don't always feel the need to drink until I am really thirsty",
  Accuracy_Gastric_Q5 = "I often feel hungry even if I ate recently",
  Accuracy_Gastric_Q6 = "I don't always feel the need to eat until I am really hungry",
  Accuracy_Gastric_Q7 = "I often sneeze suddenly without feeling the need building up",
  Accuracy_Gastric_Q8 = "I sometimes feel that burping will produce some relief but then it doesn't",
  Accuracy_Genital_Q1 = "I can always accurately perceive if my genital organs are in a state of arousal (e.g., hard, wet, pulsating)",
  Accuracy_Genital_Q2 = "I sometimes feel like I am sexually aroused, but when I try to satisfy the feeling, I realise that I am not as sexually aroused as I initially thought",
  Accuracy_Genital_A = "I can always accurately perceive that to this question I should answer the lowest option",
  Accuracy_SkinThermo_Q1 = "I can always accurately feel when something is going to be itchy",
  Accuracy_SkinThermo_Q2 = "I can always accurately feel when I start to have a fever",
  Accuracy_SkinThermo_Q3 = "When something touches my skin, I can always accurately feel if it's hot or cold",
  Accuracy_SkinThermo_Q4 = "I sometimes feel my skin itching, but when I scratch it, it doesn't produce the relief I expected",
  Accuracy_ColonBladder_Q1 = "I often feel the need to urinate even when my bladder is not full",
  Accuracy_ColonBladder_Q2 = "I don't always feel the need to urinate until my bladder is very full",
  Accuracy_ColonBladder_Q3 = "I often feel the need to defecate even when my intestine is not full",
  Accuracy_ColonBladder_Q4 = "I don't always feel the need to defecate until my intestine is very full",
  Accuracy_ColonBladder_Q5 = "I sometimes feel like I need to urinate or defecate but when I go to the bathroom I produce less than I expected",
  Confusion_State_Q1 = "Sometimes I can't tell if the sensations in my body are good or bad",
  Confusion_State_Q2 = "Sometimes I am confused about what sensations in my body mean",
  Confusion_Cardiac_Q1 = "Sometimes my heart starts racing and I often don't know why",
  Confusion_Respiratory_Q1 = "Sometimes my breathing becomes erratic or shallow and I often don't know why",
  Confusion_Gastric_Q1 = "Sometimes I feel negative and realise after eating that I was just hungry",
  Confusion_Gastric_Q2 = "Sometimes I don't realise I was hungry until I ate something",
  Confusion_Genital_Q1 = "Sometimes I notice arousal in my genital areas (e.g., stiffness, wetness) when I am not feeling sexually aroused",
  Confusion_SkinThermo_Q1 = "Sometimes I have sensations on my skin (e.g., itches, goosebumps) without any clear cause",
  Confusion_ColonBladder_Q1 = "Sometimes I am not sure whether I need to go to the toilet or not (to urinate or defecate)",
  Confusion_ColonBladder_A = "Sometimes I notice that I need to answer all the way to the right"
)
```

## Item Correlation

### Full Sample

```{r}
#| fig-width: 12
#| fig-height: 12

make_heatmap <- function(items, interactive=TRUE, title="Correlation Matrix") {
  fn <- if(interactive) heatmaply::heatmaply else heatmaply::ggheatmap

  fn(
    cor(items),
    symm = TRUE,
    colors=heatmaply::cool_warm,
    show_dendrogram =c(FALSE, TRUE),
    main=title,
    showticklabels = FALSE,
    hide_colorbar = TRUE,
    k_col = 4,
    # k_row = 4,
    limits = c(-1, 1)
    )
}

make_heatmap(items, title="Full Sample")
```

### Similarity

```{r}
#| eval: true

bootstrap_similarity <- function(df) {
  rez <- data.frame()
  for(i in 1:200) {
    idx <- sample(1:nrow(df), nrow(df), replace=TRUE)
    newdata <- df[idx,]
    items <- select(df, contains("_Q"))
    byfacet <- items[newdata$Condition=="Dimensions",]
    bymodality <- items[newdata$Condition=="Domains",]
    byrandom <- items[newdata$Condition=="Random",]

    rez <- rbind(
      MatrixCorrelation::allCorrelations(cor(byrandom), cor(byfacet),
                                         ncomp1=10, ncomp2=10, plot=FALSE),
      MatrixCorrelation::allCorrelations(cor(byrandom), cor(bymodality),
                                         ncomp1=10, ncomp2=10, plot=FALSE),
      MatrixCorrelation::allCorrelations(cor(items), cor(byfacet),
                                         ncomp1=10, ncomp2=10, plot=FALSE),
      MatrixCorrelation::allCorrelations(cor(items), cor(bymodality),
                                         ncomp1=10, ncomp2=10, plot=FALSE)) |>
      as.data.frame() |>
      mutate(
        Comparison = c("Random vs. Facet", "Random vs. Modality", "Full vs. Facet", "Full vs. Modality"),
        Sample = c("Random", "Random", "Full", "Full"),
        Iteration = i) |>
      mutate(d_PSI = diff(PSI), d_RVadj = diff(RVadj), d_SMI = diff(SMI), .by="Sample") |>
      rbind(rez)
  }
  rez
}

rez <- bootstrap_similarity(df)
```

```{r}
#| fig-width: 10
#| fig-height: 10

rez |>
  pivot_longer(-c("Comparison", "Sample", "Iteration")) |>
  filter(name %in% c("PSI", "RVadj", "SMI")) |>
  mutate(side = ifelse(str_detect(Comparison, "Facet"), "left", "right")) |>
  ggplot(aes(x=name, y=value, fill=Comparison, color=Comparison)) +
  ggdist::stat_halfeye(aes(side=side), position=position_dodge(width=0.3), alpha=0.7) +
  facet_wrap(~Sample) +
  scale_fill_manual(values=c("Random vs. Facet"="#F44336", "Random vs. Modality"="#2196F3", "Full vs. Facet"="#FF5722", "Full vs. Modality"="#00BCD4")) +
  scale_color_manual(values=c("Random vs. Facet"="#F44336", "Random vs. Modality"="#2196F3", "Full vs. Facet"="#FF5722", "Full vs. Modality"="#00BCD4")) +
  labs(x="Indices of Correlation Matrix Difference", y="Similarity") +
  theme_minimal()
```

```{r corsimilarity}
#| fig-width: 10
#| fig-height: 10
#| fig-dpi: 200

p_sim <- rez |>
  pivot_longer(-c("Comparison", "Sample", "Iteration")) |>
  filter(str_detect(name, "d_") & str_detect(Comparison, "Facet")) |>
  filter(Sample == "Random") |>
  ggplot(aes(x=value, y=name)) +
  ggdist::stat_eye(aes(fill = after_stat(x < 0))) +
  geom_vline(xintercept=0, linetype="dashed") +
  labs(x="Similarity Difference", y="Indices of pattern difference",
       title="To which matrix is the random one more similar?",
       fill="More similar to") +
  theme_minimal() +
  scale_fill_manual(values=c("TRUE"="#2196F3", "FALSE"="#4CAF50"), labels = c("By modality", "By facet"))

r <- correlation::cor_sort(cor(byrandom))
order <- colnames(r)

make_corplot <- function(data, order) {
  rownames_to_column(as.data.frame(cor(data)), "item") |>
    pivot_longer(-item) |>
    mutate(item = fct_relevel(item, order),
           name = fct_relevel(name, order)) |>
    ggplot(aes(x=name, y=item, fill=value)) +
    geom_tile() +
    # scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0, values=c(-1, 0, 1)) +
    scale_fill_gradientn(
      colors=c("blue", "white", "#FFEE58", "#FFC107", "#FF9800", "#FF5722",
               "#F44336", "#E91E63", "#9C27B0", "#8231B4", "#673AB7", "white"),
      values=c(-1, seq(0, 1, 0.1))) +
    theme_minimal() +
    theme(axis.text = element_blank(),
          axis.title = element_blank(),
          legend.position = "none")
}

p1 <- make_corplot(byrandom, order) +
  ggtitle("Grouped randomly")
p2 <- make_corplot(byfacet, order) +
  ggtitle("Grouped by facet")
p3 <- make_corplot(bymodality, order) +
  ggtitle("Grouped by modality")

p1 / (p2 | p_sim | p3) +
  patchwork::plot_layout(heights=c(3, 1)) +
  patchwork::plot_annotation(
    title="Effect of Item-presentation Grouping",
    theme = theme(plot.title = element_text(hjust = 0.5, face="bold")))
```

## Item Selection

### Unique Variable Analysis (UVA)

```{r}
#| fig-width: 10
#| fig-height: 8

uva <- EGAnet::UVA(items, cut.off = 0.25, reduce.method="remove", verbose=FALSE)

toremove1 <- unique(uva$keep_remove$remove)
keep <- uva$keep_remove$keep[!uva$keep_remove$keep %in% toremove1]

sorted <- correlation::cor_sort(cor(items[toremove1],items[keep]))

correlation::correlation(items[toremove1], items[keep]) |>
  mutate(Parameter1 = fct_relevel(Parameter1, rownames(sorted)),
         Parameter2 = fct_relevel(Parameter2, colnames(sorted))) |>
  ggplot(aes(x=Parameter1, y=Parameter2, fill=r)) +
  geom_tile() +
  geom_text(aes(label=insight::format_value(r)), color="white") +
  scale_fill_gradient2(low="blue", high="red", mid="white", midpoint=0, guide="none") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x="Removed Items", y="Kept Items", fill="Correlation")
```

```{r}
items <- select(items, -all_of(toremove1))
byfacet <- select(byfacet, -all_of(toremove1))
bymodality <- select(bymodality, -all_of(toremove1))
byrandom <- select(byrandom, -all_of(toremove1))
```

@@

# plot(itemstability)
```

```{r}
itemstability_table |>
  select(-Cluster, -Max) |>
  gt::gt() |>
  gt::data_color(columns=-Item,
                 method = "numeric",
                 palette = c("white", "orange", "green"),
                 domain = c(0, 1)) |>
  gt::data_color(columns=Item, fn=\(x) ifelse(x %in% toremove2, "#FFEBEE", "white")) |>
  gt::tab_header(
    title = gt::md("**Item Stability**"),
    subtitle = "Proportion of times an item is assigned to the same cluster"
  ) |>
  gt::fmt_number(columns=-Item, decimals=3)
```

```{r}
items <- select(items, -all_of(toremove2))
byfacet <- select(byfacet, -all_of(toremove2))
bymodality <- select(bymodality, -all_of(toremove2))
byrandom <- select(byrandom, -all_of(toremove2))
```

### Item Loadings

ega2 <- bootEGA(
  items,
  EGA.type = "hierEGA",
  model = "glasso",  # BGGM
  algorithm = "leiden",  # walktrap
  type="resampling",
  plot.itemStability=FALSE,
  typicalStructure=TRUE,
  plot.typicalGraph=FALSE,
  iter=500,
  seed=3, ncores = 4)

save(ega2, file="models/ega2.RData")
```

load("models/ega2.RData")

plot(itemStability(ega2, IS.plot=FALSE))

# itemstability_table <- make_loadingtable(itemstability$lower_order$item.stability$all.dimensions)
# toremove2 <- filter(itemstability_table, Max < 0.7)$Item
```

```{r}
#| message: false

lower <- make_loadingtable(net.loads(ega2$EGA$lower_order)$std)

toremove3 <- lower$Item[!lower$Item %in% slice_max(lower, Max, n=3, by="Cluster")$Item]

lower |>
  select(-Cluster, -Max) |>
  gt::gt() |>
  gt::data_color(columns=-Item,
                 method = "numeric",
                 palette = c("red", "white", "green"),
                 domain = c(-1, 1)) |>
  gt::data_color(columns=Item, fn=\(x) ifelse(x %in% toremove3, "#FFEBEE", "white")) |>
  gt::tab_header(
    title = gt::md("**Item Loadings**"),
    subtitle = "Node centrality"
  ) |>
  gt::fmt_number(columns=-Item, decimals=3)
```

```{r}
items <- select(items, -all_of(toremove3))
byfacet <- select(byfacet, -all_of(toremove3))
bymodality <- select(bymodality, -all_of(toremove3))
byrandom <- select(byrandom, -all_of(toremove3))
```

## Structure Analysis

ega3 <- bootEGA(
  items,
  EGA.type = "hierEGA",
  model = "glasso",  # BGGM
  algorithm = "leiden",  # walktrap
  type="resampling",
  plot.itemStability=FALSE,
  typicalStructure=TRUE,
  plot.typicalGraph=TRUE,
  iter=500,
  seed=3, ncores = 4)

save(ega3, file="models/ega3.RData")
```

load("models/ega3.RData")

plot(itemStability(ega3))
```

### Item Table

```{r}
#| message: false

dimensions <- list(
  C01 = "UrIn",       # Urointestinal Inaccuracy
  C09 = "CaCo",       # Cardiorespiratory Confusion
  C13 = "CaNo",       # Cardiorespiratory Noticing
  C18 = "Olfa",       # Olfactory Compensation
  C03 = "Sati",       # Satiety Noticing
  C04 = "SexA",       # Sexual Arousal Awareness
  C06 = "SexS",       # Sexual Arousal Sensitivity
  C15 = "SexO",       # Sexual Organs Sensitivity
  C08 = "UrSe",       # Urointestinal Sensitivity
  C10 = "RelA",       # Relaxation Awareness
  C05 = "StaS",       # State Specificity
  C02 = "ExAc",       # Expulsion Accuracy
  C17 = "Card",       # Cardioception
  C14 = "Resp",       # Respiroception
  C12 = "Sign",       # Signalling
  C16 = "Gast",       # Gastroception
  C11 = "Derm",       # Dermatoception
  C07 = "SexC"        # Sexual Arousal Changes
)

higher <- make_loadingtable(t(net.loads(ega3$EGA$higher_order, loading.method="revised")$std))
cluster_order <- names(higher)[!names(higher) %in% c("Item", "Cluster", "Max")]

lower <- make_loadingtable(net.loads(ega3$EGA$lower_order, loading.method="revised")$std) |>
  select(names(higher)) |>
  mutate(Cluster = fct_relevel(Cluster, cluster_order)) |>
  arrange(Cluster, desc(Max))

higher$Item <- paste0("M", higher$Item)
higher$Label <- c("Interoceptive Deficit", "Interoceptive Awareness", "Interoceptive Sensitivity")
lower <- mutate(lower, Label = labels[Item], ID= Item, Item = 1:n())

tab1 <- rbind(higher, select(lower, -ID)) |>
  datawizard::data_relocate("Label", after = "Item") |>
  select(-Cluster, -Max) |>
  # datawizard::data_rename(dimensions) |>  # https://github.com/easystats/datawizard/issues/576
  datawizard::data_rename(names(dimensions), dimensions) |> 
  mutate(`|` = "") |> 
  gt::gt() |>
  gt::tab_row_group(
    label = "Items",
    rows = 1:(nrow(lower) + nrow(higher))
  ) |>
  gt::tab_row_group(
    label = "Metaclusters",
    rows = 1:nrow(higher)
  ) |>
  gt::data_color(columns=-Item,
                 method = "numeric",
                 palette = c("red", "white", "green"),
                 domain = c(-1, 1)) |>
  gt::tab_style(
    style = gt::cell_text(size="small", style="italic"),
    locations = gt::cells_body(columns="Label", rows=c(4:57))
  ) |>
  gt::tab_style(
    style = list(gt::cell_text(weight="bold"),
                 gt::cell_fill(color = "#F5F5F5")),
    locations = list(
      gt::cells_row_groups(groups = "Items"),
      gt::cells_row_groups(groups = "Metaclusters")
    )
  ) |>
  # Metacluster 1
  gt::tab_style(
    style = gt::cell_fill(color = "#B39DDB"),
    locations = list(
      gt::cells_column_labels(columns = 3),
      gt::cells_body(columns="Item", rows=c(4:6))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#9FA8DA"),
    locations = list(
      gt::cells_column_labels(columns = 4),
      gt::cells_body(columns="Item", rows=c(7:9))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#90CAF9"),
    locations = list(
      gt::cells_column_labels(columns = 5),
      gt::cells_body(columns="Item", rows=c(1, 10:12))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#81D4FA"),
    locations = list(
      gt::cells_column_labels(columns = 6),
      gt::cells_body(columns="Item", rows=c(13:15))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#80DEEA"),
    locations = list(
      gt::cells_column_labels(columns = 7),
      gt::cells_body(columns="Item", rows=c(16:18))
    )
  ) |>
  # Metacluster 2
  gt::tab_style(
    style = gt::cell_fill(color = "#F3F29D"),
    locations = list(
      gt::cells_column_labels(columns = 8),
      gt::cells_body(columns="Item", rows=c(19:21))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#E6EE9C"),
    locations = list(
      gt::cells_column_labels(columns = 9),
      gt::cells_body(columns="Item", rows=c(22:24))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#D6E8A1"),
    locations = list(
      gt::cells_column_labels(columns = 10),
      gt::cells_body(columns="Item", rows=c(25:27))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#C5E1A5"),
    locations = list(
      gt::cells_column_labels(columns = 11),
      gt::cells_body(columns="Item", rows=c(2, 28:30))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#B5DCA6"),
    locations = list(
      gt::cells_column_labels(columns = 12),
      gt::cells_body(columns="Item", rows=c(31:33))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#A5D6A7"),
    locations = list(
      gt::cells_column_labels(columns = 13),
      gt::cells_body(columns="Item", rows=c(34:36))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#93D1B6"),
    locations = list(
      gt::cells_column_labels(columns = 14),
      gt::cells_body(columns="Item", rows=c(37:39))
    )
  ) |>
  # Metacluster 3
  gt::tab_style(
    style = gt::cell_fill(color = "#CE93D8"),
    locations = list(
      gt::cells_column_labels(columns = 15),
      gt::cells_body(columns="Item", rows=c(40:42))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#F48FB1"),
    locations = list(
      gt::cells_column_labels(columns = 16),
      gt::cells_body(columns="Item", rows=c(43:45))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#EF9A9A"),
    locations = list(
      gt::cells_column_labels(columns = 17),
      gt::cells_body(columns="Item", rows=c(3, 46:48))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#FFAB91"),
    locations = list(
      gt::cells_column_labels(columns = 18),
      gt::cells_body(columns="Item", rows=c(49:51))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#FFCC80"),
    locations = list(
      gt::cells_column_labels(columns = 19),
      gt::cells_body(columns="Item", rows=c(52:54))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#FFE082"),
    locations = list(
      gt::cells_column_labels(columns = 20),
      gt::cells_body(columns="Item", rows=c(55:57))
    )
  ) |>
  gt::fmt_number(columns=-Item, decimals=2) |>
  gt::tab_header(
    title = gt::md("**Item Loadings**"),
    subtitle = "Node centrality"
  ) |> 
  gt::opt_vertical_padding(scale = 0.7) |>
  gt::opt_horizontal_padding(scale = 0.5) |>
  # gt::tab_options(table.width = gt::pct(100)) |> 
  gt::cols_width(Label ~ gt::pct(66),
                 `|` ~ gt::pct(1))

gt::gtsave(gt::cols_hide(tab1, `|`), "table1.html", inline_css = TRUE) # Save it and reload it otherwise formatting not ideal

Sys.setenv(CHROMOTE_CHROME = "C:\\Program Files (x86)\\Microsoft\\Edge\\Application\\msedge.exe")

gt::gtsave(tab1, "table1.png", vwidth=1660, expand=0, quiet=TRUE)
```

<object type="text/html" data="table1.html" width="125%" height="1000"></object>

<!-- ![](table1.png) -->

### Graph

```{r}
# REMOVE ONCE https://github.com/hfgolino/EGAnet/pull/167 is merged
convert2tidygraph <- function(EGA.object)
{

  if("bootEGA" %in% class(EGA.object)) {
    # Bootstrapped EGA ---
    if(!"typicalGraph" %in% names(EGA.object)) {
      stop("The bootEGA object must contain a typicalGraph object. Set `typicalStructure=TRUE`.")
    }

    if("lower_order" %in% names(EGA.object$typicalGraph)) {
      # Hierarchical EGA ---
      lower_nodes <- .convert2tidygraph_nodes(EGA.object$typicalGraph$lower_order$wc)
      lower_nodes$dimension <- paste0("L", lower_nodes$dimension)  # Discriminate from higher
      lower_nodes$level <- "Lower"
      higher_nodes <- .convert2tidygraph_nodes(EGA.object$typicalGraph$higher_order$wc)
      higher_nodes$name <- paste0("L", as.numeric(higher_nodes$name))
      higher_nodes$dimension <- paste0("H", higher_nodes$dimension)  # Discriminate from lower
      higher_nodes$level <- "Higher"
      nodes <- rbind(lower_nodes, higher_nodes)

      lower_edges <- .convert2tidygraph_edges(EGA.object$typicalGraph$lower_order$graph)
      higher_edges <- .convert2tidygraph_edges(EGA.object$typicalGraph$higher_order$graph)
      higher_edges$from <- paste0("L", as.numeric(higher_edges$from))
      higher_edges$to <- paste0("L", as.numeric(higher_edges$to))
      edges <- rbind(lower_edges, higher_edges)
      edges$type <- "real"

      # Make edges from lower to higher order
      for(i in 1:nrow(lower_nodes)) {
        edges <- rbind(
          edges,
          data.frame(from = lower_nodes$name[i], to = lower_nodes$dimension[i], link = 1, type = "virtual")
          )
      }
    } else {
      # Non-hierarchical EGA ---
      nodes <- .convert2tidygraph_nodes(EGA.object$typicalGraph$wc)
      edges <- .convert2tidygraph_edges(EGA.object$typicalGraph$graph)
    }

  } else {
    # Normal EGA ---
    nodes <- .convert2tidygraph_nodes(EGA.object$wc)
    edges <- .convert2tidygraph_edges(EGA.object$network)
  }

  # Return result
  return(
    list(
      nodes = nodes,
      edges = edges[edges$link != 0,]
    )
  )
}

#' @keywords internal
#' @noRd
.convert2tidygraph_nodes <- function(wc){
  data.frame(
    name = names(wc),
    dimension = as.character(wc)
  )
}

#' @keywords internal
#' @noRd
.convert2tidygraph_edges <- function(network){
  data.frame(
    from = rep(rownames(network), times = ncol(network)),
    to = rep(colnames(network), each = nrow(network)),
    link = as.vector(network)
  )
}
```

```{r graph}
#| fig-width: 9
#| fig-height: 8
#| fig-dpi: 200

#| warning: false

graph <- convert2tidygraph(ega3)

replace_lowernames <- function(names, lower) {
  rownames(lower) <- lower$ID
  sprintf("%02d", as.numeric(lower[names, "Item"]))
}
replace_highernames <- function(names) {
  x <- as.numeric(str_remove(names, "L"))  
  paste0("C", sprintf("%02d", x))
}

# Arrange lower nodes in circle
lower_nodes <- graph$nodes |> 
  filter(level == "Lower") |> 
  mutate(name = fct_relevel(name, as.character(lower$ID)),
         ID = name) |> 
  arrange(name)  
lower_edges <- graph$edges |> 
  filter(from %in% lower_nodes$name & to %in% lower_nodes$name)
lower_layout <- tidygraph::tbl_graph(lower_nodes, edges=lower_edges, directed=FALSE) |> 
  ggraph::create_layout(layout = 'circle') |> 
  as.data.frame()
rownames(lower_layout) <- lower_nodes$name

>>>>

---
title: "InteroceptionScale (study 2) - Data Analysis"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
execute: 
  cache: true
---

@@

df <- read.csv("../data/data_participants.csv")
```

## Structure Validation

items <- select(df, starts_with("MINT_"))
```

```{r}
labels <- list(
  MINT_Deficit_CaCo_4 = "Sometimes my breathing becomes erratic or shallow and I often don't know why",
  MINT_Deficit_CaCo_5 =  "I often feel like I can't get enough oxygen by breathing normally"
)
# TODO
```

@@
